FraCaS: Temporal Analysis

### 2020-05-04 paper2020/paper.tex
minor comments

We use notions of ``stative'', ``achievement'', ``activity''. Our
definition do not seem to match perfectly the definitions found in the
literature; however we think they are good definitions, given that
they generally afford the correct inferences for the testsuite. (We
assume the testsuite is correct.)

@@

(The difference between actitivty and achievement is that for the
latter time intervals can be assumed to be of nil\footnote{TODO: needs qualification} duration. However
this appears to play little role, if any, in our analysis.)

@@

\[\begin{array}{l}
∃x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃y. novel(y) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,y,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\]
Our analysis does not need to treat this last case specially. Indeed,
even if $write(smith,x,.,.)$ is an activity and thus subject to
unicity of action, in (280), $x$ is quantified existentially; we have
two \emph{different} actions: $write(smith,x,t_1,t_2)$ and
$write(smith,y,t_3,t_4)$, because $x \neq y$, and thus we cannot deduce equality of the
intervals $t_1,t_2$ and $t_3,t_4$. In turn, the hypothesis cannot be refuted.

>>>>

We use notions of ``stative'', ``achievement'', ``activity''. Our
definition do not seem to match perfectly the definitions found in the
literature; In general, we use the term achievement to include accomplishment as well. Insofar as the test suite is concerned, we find that these two categories can be collapsed into a single one.  As such,  we think it is  a good classification, given that
they generally afford the correct inferences for the testsuite. (We
assume the testsuite is correct.)

@@

(The difference between actitivty and achievement is that for the
latter time intervals can be assumed to be of nil duration. In reality, this is an oversimplification as achievements are usually of short duration. but not nil. However, 
this appears to play little role, if any, in our analysis, and given the task-driven nature of it as well.)

@@

\[\begin{array}{l}
∃x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃y. novel(y) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,y,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\]
Our analysis does not need to treat this last case specially. Indeed,
even if $write(smith,x,.,.)$ is an activity \todo{This should be an accomplishment and thus, achievement in our classification} and thus subject to
unicity of action, in (280), $x$ is quantified existentially; we have
two \emph{different} actions: $write(smith,x,t_1,t_2)$ and
$write(smith,y,t_3,t_4)$, because $x \neq y$, and thus we cannot deduce equality of the
intervals $t_1,t_2$ and $t_3,t_4$. In turn, the hypothesis cannot be refuted.
